---
title: "p8105_hw5_st3431"
output: github_document
date: "2022-11-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(tidyverse)
```

**Problem 2** 

The raw data has variables such as the date of the crime, the victims names, the location which the crime was occurring and the outcome of the crime (whether it was solved or remained unsolved). 

Importing and cleaning the dataset
```{r}
crimes_df =
  read_csv("hw5_data/homicide-data.csv", na = c("", "Unknown")) %>%
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved")) %>% 
  relocate(city_state)  
 
```

Unsolved homicides in Baltimore, MD 

```{r}
baltimore_df =
  crimes_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_crimes =
  baltimore_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n())

baltimore_prop =
  prop.test(
    x = baltimore_crimes %>% pull(unsolved),
    n = baltimore_crimes %>% pull(n)) 

  broom::tidy(baltimore_prop) %>% 
  select(estimate, conf.low, conf.high) %>% 
  knitr::kable()
```

The estimated proportion of unsolved cases within Baltimore, Marlyand is 64.56% with a 95% confidence interval of (62.76%, 66.32%). 


Unsolved cases across each city 

```{r}
prop_test_function = function(city_df) {
  city_totals =
    city_df %>% 
      summarize(
        unsolved = sum(resolution == "unsolved"),
        n = n())
    city_prop =
    prop.test(
      x = city_totals %>% pull(unsolved),
      n = city_totals %>% pull(n))
 return(city_prop) }

prop_test_function(baltimore_df)


all_cities=
  crimes_df %>% 
  nest(data = uid:resolution) %>%
  mutate(
    results = map(data, prop_test_function), 
    tidy_results= map(results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, conf.low, conf.high) %>%  
  rename(low_conf= conf.low, high_conf= conf.high)
  
```


Creating a plot showing estimates and CI's for each city


```{r}
all_cities %>%  
  mutate(city_state= fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x= city_state, y= estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin= low_conf, ymax= high_conf)) + 
  labs(title= "Estimates of Unsolved Cases in 50 U.S. Cities", 
       x= "City", 
       y= "Estimates of Unsolved Cases") +
  coord_flip()
  
```


**Problem 3** 

**Problem 3**

```{r}
library(rvest)

sample_df = map(1:5000, ~ rnorm(n = 30, mean = 0, sd = 5))

est_mean = function(n_obs = 30, mu, sigma = 5) {
  x = rnorm(n = n_obs, mean = mu, sd = sigma)
  tibble (mu_mean = mean(x),
    p_value = t.test(x, mu = 0)$p.value
  )
  
}

df_mu = 
  expand_grid(n = 30,
    mu = 0,
    sigma = 5,
    dataset = 1:5000) %>% 
  mutate( estimates_df = 
      map(.x = mu, ~est_mean(mu = .x))) %>% 
  unnest(estimates_df)

df_mu

all_mu = 
  expand_grid(
    n = 30,
    mu = c(1, 2, 3, 4, 5, 6), 
    sigma = 5,
    dataset = 1:5000) %>% 
  mutate(
    estimates_df = 
      map(.x = mu, ~est_mean(mu = .x))) %>% 
  unnest(estimates_df)

all_mu
```


```{r}
Plot_1 = 
  all_mu %>%
  group_by(mu) %>%
  summarise(
    null_reject = sum(p_value < 0.05),
    cnt = n()) %>%
  mutate(
    prop_null_reject = null_reject / cnt)  %>% 
  ggplot(aes(x = mu, y = prop_null_reject)) + 
  geom_point(alpha=0.5) + 
  geom_line(alpha=0.5) +
  labs(
    title = "Null Hypothesis Rejection Proportion by Sample Mean",
    x = "True Sample Mean Value",
    y = "Null Hypothesis Rejection Proportion")

Plot_1
```

The relationship between the true sample mean and the power is a positive one. As the true sample mean increases the power increases and as the sample mean reaches 5 the power hits 1. We can then conclude that large effect sizes increase statistical power. 

```{r}
library(patchwork)
Plot_2a= 
  all_mu %>%
  group_by(mu) %>%
  mutate(avg_mu = mean(mu_mean)) %>%
  ggplot(aes(x = mu, y = avg_mu)) +
  geom_point() + 
  geom_line(alpha= .5) +
  labs(
    title = "Average Estimated Sample Mean vs. True Sample Mean",
    x = "True Sample Mean",
    y = "Average Estimated Sample Mean")

Plot_2a

Plot_2b= 
 all_mu %>%
  filter(p_value < 0.05) %>%
  group_by(mu) %>%
  mutate(avg_mu = mean(mu_mean)) %>%
  ggplot(aes(x = mu, y = avg_mu)) +
  geom_point() + 
  geom_line(alpha= 0.5) + 
  labs(
    title = "Average Estimated Sample Mean vs. True Sample Mean in Rejected Samples",
    x = "True Sample Mean",
    y = "Avg Estimated Sample Mean")

Plot_2b

Plot_2a + Plot_2b
```

Comparing the two plots we can see that the true sample mean is approximately equal to the average sample mean when we include all of the samples. However when we only include the sample that is rejected in plot 2b, there are fewer values that align with the true value.    

